Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-18 providence/sections/workload.tex
add error bars to fig 6
avg bals ratio with error bars
errorbars
combined misleading plot

\subsubsection{Average total ballots.} 
The simplest workload models are a function of just the total number of a ballots sampled.\footnote{Sometimes total \emph{distinct} ballots sampled is used, but for the margins we use in our examples in this section, the difference between total distinct ballots and total ballots is insignificant\cite{arxiv_athena}. It is straightforward to modify the model we discuss here to account for total distinct ballots.} Figure~\ref{fig:avg_bals} shows the average total number of ballots sampled as a function of $p$.
\begin{figure}[h!]
\includegraphics[width=.5\textwidth]{avg_bals.png}
\caption{The total number of ballots sampled on average, as a function of $p$, the conditional stopping probability used to select each round size, for ballot polling audits of the 2020 US Presidential election in the state of Virginia.}
\label{fig:avg_bals}
\end{figure}

Figure~\ref{fig:avg_bals_ratio} provides the same number as a fraction of the \Providence values.
It is straightforward to show that \Providence and both forms of \BRAVO collapse to the same test when each round corresponds to a single ballot. Figures~\ref{fig:avg_bals} and \ref{fig:avg_bals_ratio} show that for larger stopping probabilities $p$ (i.e. larger rounds), \Providence requires fewer ballots on average. In particular, the savings of \Providence become larger as $p$ increases; for $p=0.95$, EoR \BRAVO and SO \BRAVO require more than $2$ and $1.4$ times as many ballots as \Providence respectively. 
\begin{figure}[h!]
\includegraphics[width=.5\textwidth]{avg_bals_ratio.png}
\caption{The total number of ballots sampled on average, as a fraction of those sampled by \Providence, as a function of $p$, the conditional stopping probability used to select each round size, for ballot polling audits of the 2020 US Presidential election in the state of Virginia.}
\label{fig:avg_bals_ratio}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=.5\textwidth]{with_round_workload.png}
\caption{For workload parameters $w_b=1$ and $w_r=1000$, this plot shows the expected workload for various values of $p$. Expected workload is found using Equation~\ref{eq:round_workload} and the average number of ballots and rounds in our simulations as the expected number of ballots and rounds.}
\label{fig:with_round_workload}
\end{figure}

@@

Figure~\ref{fig:optimal_workloads} shows the optimal achievable workload for a wide range of per round workloads. For very low round workloads, the workload function approaches just the total number of ballots, and so workload is minimized by minimizing the number of ballots drawn, which corresponds to small round sizes, and we would expect all three audits to behave similarly, as ballot-by-ballot audits, with the smallest workload. On the other hand, for extremely large values of round workload, the average number of ballots has little impact on the workload function, and so the three audits again have similar values, all corresponding to large round sizes in order to minimize the number of rounds.  We know that there is variation in the number of ballots used by each type of audit for large round sizes (a factor of two for $p=0.9$), but these values would be small in comparison to $w_r$. We observe this behaviour in Figure~\ref{fig:optimal_workloads} for extremely small and large workload values. For more reasonable values of the round workload $w_r$, SO \BRAVO and EoR \BRAVO achieve minimum workload roughly $1.1$ and $1.3$ times greater than that of \Providence.
\begin{figure}[h!]
\includegraphics[width=.5\textwidth]{optimal_workloads.png}
\caption{For varying round workload $w_r$, the optimal average workload achievable by each audit, as a fraction of the \Providence values.}
\label{fig:optimal_workloads}
\end{figure}

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{misleading_limits.png}
\caption{The proportion of simulated \Providence audits for the Virginia contest parameters that had a \emph{misleading sample} in any round.}
\label{fig:misleading}
\end{figure}

We observe a similar behavior in our simulations of audits on the contest from the pilot audit. Figure~\ref{fig:pilot_misleading} shows the proportion of the pilot simulations which contained a \emph{misleading sample} in any round. Despite the large difference in margin ($\sim 0.05$ in Virginia and $\sim 0.25$ in the pilot) we still observe that a \emph{misleading limit} of $0.01$ is first achieved at roughly $p=0.8$ and $0.001$ at $p=0.95$.

\begin{figure}
\includegraphics[width=.5\textwidth]{pilot_misleading_prop.png}
\caption{The proportion of simulated \Providence audits for the pilot audit parameters that had a \emph{misleading sample} in any round.}
\label{fig:pilot_misleading}
\end{figure}

>>>>

\subsubsection{Average total ballots.} 
The simplest workload models are a function of just the total number of a ballots sampled.\footnote{Sometimes total \emph{distinct} ballots sampled is used, but for the margins we use in our examples in this section, the difference between total distinct ballots and total ballots is insignificant\cite{arxiv_athena}. It is straightforward to modify the model we discuss here to account for total distinct ballots.} Figure~\ref{fig:avg_bals} shows the average total number of ballots sampled as a function of $p$.
\begin{figure}[h!]
%\includegraphics[width=.5\textwidth]{avg_bals.png}
\includegraphics[width=.5\textwidth]{avg_bals_error_bars_every_three.png}
\caption{The total number of ballots sampled on average, as a function of $p$, the conditional stopping probability used to select each round size, for ballot polling audits of the 2020 US Presidential election in the state of Virginia.}
\label{fig:avg_bals}
\end{figure}

Figure~\ref{fig:avg_bals_ratio} provides the same number as a fraction of the \Providence values.
It is straightforward to show that \Providence and both forms of \BRAVO collapse to the same test when each round corresponds to a single ballot. Figures~\ref{fig:avg_bals} and \ref{fig:avg_bals_ratio} show that for larger stopping probabilities $p$ (i.e. larger rounds), \Providence requires fewer ballots on average. In particular, the savings of \Providence become larger as $p$ increases; for $p=0.95$, EoR \BRAVO and SO \BRAVO require more than $2$ and $1.4$ times as many ballots as \Providence respectively. 
\begin{figure}[h!]
%\includegraphics[width=.5\textwidth]{avg_bals_ratio.png}
\includegraphics[width=.5\textwidth]{avg_bals_ratio_errorbars.png}
\caption{The total number of ballots sampled on average, as a fraction of those sampled by \Providence, as a function of $p$, the conditional stopping probability used to select each round size, for ballot polling audits of the 2020 US Presidential election in the state of Virginia.}
\label{fig:avg_bals_ratio}
\end{figure}

@@

\begin{figure}[h!]
%\includegraphics[width=.5\textwidth]{with_round_workload.png}
\includegraphics[width=.5\textwidth]{with_round_workload_errorbars.png}
\caption{For workload parameters $w_b=1$ and $w_r=1000$, this plot shows the expected workload for various values of $p$. Expected workload is found using Equation~\ref{eq:round_workload} and the average number of ballots and rounds in our simulations as the expected number of ballots and rounds.}
\label{fig:with_round_workload}
\end{figure}

@@

Figure~\ref{fig:optimal_workloads} shows the optimal achievable workload for a wide range of per round workloads. For very low round workloads, the workload function approaches just the total number of ballots, and so workload is minimized by minimizing the number of ballots drawn, which corresponds to small round sizes, and we would expect all three audits to behave similarly, as ballot-by-ballot audits, with the smallest workload. On the other hand, for extremely large values of round workload, the average number of ballots has little impact on the workload function, and so the three audits again have similar values, all corresponding to large round sizes in order to minimize the number of rounds.  We know that there is variation in the number of ballots used by each type of audit for large round sizes (a factor of two for $p=0.9$), but these values would be small in comparison to $w_r$. We observe this behaviour in Figure~\ref{fig:optimal_workloads} for extremely small and large workload values. For more reasonable values of the round workload $w_r$, SO \BRAVO and EoR \BRAVO achieve minimum workload roughly $1.1$ and $1.3$ times greater than that of \Providence.
\begin{figure}[h!]
%\includegraphics[width=.5\textwidth]{optimal_workloads.png}
\includegraphics[width=.5\textwidth]{optimal_workloads.png}
\caption{For varying round workload $w_r$, the optimal average workload achievable by each audit, as a fraction of the \Providence values.}
\label{fig:optimal_workloads}
\end{figure}

@@

\begin{figure}
%\includegraphics[width=.5\textwidth]{misleading_limits.png}
\includegraphics[width=.5\textwidth]{combined_misleading.png}
\caption{The proportion of simulated \Providence audits for the Virginia and pilot contest parameters that had a \emph{misleading sample} in any round.}
\label{fig:misleading}
\end{figure}

We observe a similar behavior in our simulations of audits on the contest from the pilot audit. Figure~\ref{fig:misleading} also shows the proportion of the pilot simulations which contained a \emph{misleading sample} in any round. Despite the large difference in margin ($\sim 0.05$ in Virginia and $\sim 0.25$ in the pilot) we still observe that a \emph{misleading limit} of $0.01$ is first achieved at roughly $p=0.8$ and $0.001$ at $p=0.95$.

%\begin{figure}
%\includegraphics[width=.5\textwidth]{pilot_misleading_prop.png}
%\caption{The proportion of simulated \Providence audits for the pilot audit parameters that had a \emph{misleading sample} in any round.}
%\label{fig:pilot_misleading}
%\end{figure}
